Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-16 paper/paper.tex
Tweak matlab section

\begin{table}[!t]
  \normalsize
  \caption{Software packages of the case study}
  \label{table:label-distribution}
  \centering
  \begin{tabular}{|l|l|l|l|}
    \hline
    \bfseries Package & \bfseries Type & \bfseries Build system & \bfseries Version \\ \hline
    preCICE & library & cmake & 2.5.0 \\ \hline
    Fortran module & bindings & make & 9e3f405 \\ \hline
    Julia bindings & bindings & julia & 2.5.0 \\ \hline
    Matlab bindings & bindings & matlab build script & 2.5.0.0 \\ \hline
    Python bindings & bindings & setup.py & 2.5.0.1 \\ \hline
    ASTE & tooling & cmake & 3.0.0 \\ \hline
    Config visualizer & tooling & setup.py & 60f2165 \\ \hline
    preCICE-CalculiX adapter & solver + adapter & makefile & 2.20 \\ \hline
    Code\_Aster & solver & custom system in python & 14.6.0 \\ \hline
    Code\_Aster-preCICE adapter & adapter & custom system in python & ce995e0 \\ \hline
    deal.II & solver & cmake & 9.4.1 \\ \hline
    preCICE-deal.II adapter & adapter & cmake & dbb25bea \\ \hline
    DUNE-FEM & solver library & setup.py & 2.8.0 \\ \hline
    preCICE-DUNE adapter& adapter & scripts + cmake & 5f2364d \\ \hline
    FEniCS & solver library& cmake + setup.py & 2019.1.0 \\ \hline
    preCICE-FEniCS adapter & adapter & setup.py & 1.4.0 \\ \hline
    Nutils & solver library & setup.py & 7.0.0 \\ \hline
    OpenFOAM & solver & wmake/Allwmake & 2206 \\ \hline
    preCICE-OpenFOAM adapter & adapter & wmake/Allwmake & 1.2.1 \\ \hline
    preCICE-SU2 adapter & solver + adapter & patch script + autoconf & 6.0.0 \\ \hline
  \end{tabular}
\end{table}

@@

\subsubsection{Matlab bindings}

There were several attempts to package matlab\footnote{\url{https://de.mathworks.com/products/matlab.html}} for NixOS in the past\footnote{\url{https://github.com/NixOS/nixpkgs/issues/56887}}, yet there was no success so far.
This might be due to the fact, that matlab needs to be installed by running an installation wizard that downloads files during the installation process and verifies the licence.
Also, as matlab is not installed in the VM, we decided to not proceed in packaging the software.

>>>>

\begin{table}[!t]
  \normalsize
  \caption{Software packages of the case study}
  \label{table:label-distribution}
  \centering
  \begin{tabular}{|l|l|l|l|}
    \hline
    \bfseries Package & \bfseries Type & \bfseries Build system & \bfseries Version \\ \hline
    preCICE & library & cmake & 2.5.0 \\ \hline
    Fortran module & bindings & make & 9e3f405 \\ \hline
    Julia bindings & bindings & julia & 2.5.0 \\ \hline
    MATLAB bindings & bindings & matlab build script & 2.5.0.0 \\ \hline
    Python bindings & bindings & setup.py & 2.5.0.1 \\ \hline
    ASTE & tooling & cmake & 3.0.0 \\ \hline
    Config visualizer & tooling & setup.py & 60f2165 \\ \hline
    preCICE-CalculiX adapter & solver + adapter & makefile & 2.20 \\ \hline
    Code\_Aster & solver & custom system in python & 14.6.0 \\ \hline
    Code\_Aster-preCICE adapter & adapter & custom system in python & ce995e0 \\ \hline
    deal.II & solver & cmake & 9.4.1 \\ \hline
    preCICE-deal.II adapter & adapter & cmake & dbb25bea \\ \hline
    DUNE-FEM & solver library & setup.py & 2.8.0 \\ \hline
    preCICE-DUNE adapter& adapter & scripts + cmake & 5f2364d \\ \hline
    FEniCS & solver library& cmake + setup.py & 2019.1.0 \\ \hline
    preCICE-FEniCS adapter & adapter & setup.py & 1.4.0 \\ \hline
    Nutils & solver library & setup.py & 7.0.0 \\ \hline
    OpenFOAM & solver & wmake/Allwmake & 2206 \\ \hline
    preCICE-OpenFOAM adapter & adapter & wmake/Allwmake & 1.2.1 \\ \hline
    preCICE-SU2 adapter & solver + adapter & patch script + autoconf & 6.0.0 \\ \hline
  \end{tabular}
\end{table}

@@

\subsubsection{MATLAB bindings}

There were several attempts to package MATLAB\footnote{\url{https://de.mathworks.com/products/matlab.html}} for NixOS in the past\footnote{\url{https://github.com/NixOS/nixpkgs/issues/56887}}, yet there was no success so far.
This might be due to the fact, that MATLAB needs to be installed by running an installation wizard that downloads files during the installation process and verifies the licence.
Also, as MATLAB is not installed in the preCICE VM, we do not proceed in packaging the software.
